---
title: "Plotting"
author: "Lilly Dipnall"
date: "06/02/2023"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "/Users/cogld/Documents/adhd_workmem/")
```

#Set Working Directory
```{r,echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/cogld/Documents/adhd_workmem/")
```

#Library
```{r}
suppressPackageStartupMessages({
  library("dplyr")
  library("tidyverse")
  library("expss")
  library("gplots")
  library("beeswarm")
  library("RColorBrewer")
  library("ggplot2")
  library("ggpubr")
  library("patchwork")
  library("table1")
  library("ggbeeswarm")
})
```
#Import Data
```{r,echo=FALSE, warning=FALSE, message=FALSE}
data <- read.csv("/Users/cogld/Documents/adhd_workmem/data.csv")
dim(data)
head(data)

fwd <- read.csv("/Users/cogld/Documents/adhd_workmem/nicap_w1_b2800_fwd.csv")
dim(fwd)
head(fwd)

data %>% full_join(fwd, by = c("id"="id"))
```
#Labelling Variables
```{r,echo=FALSE, warning=FALSE, message=FALSE}
data$group_dich <- as.factor(data$group_dich)
data$sex <- as.factor(data$sex)
data$c3_childage2 <- as.numeric(data$c3_childage2)
data$p3medcur <- as.factor(data$p3medcur)
data$handed <- as.factor(data$handed)
data$L_SLF2_tbv <- as.numeric(data$L_SLF2_tbv)
data$L_SLF2_AFD_m <- as.numeric(data$L_SLF2_AFD_m)
data$rt2_log <- as.numeric(data$rt2_log)
data$rtv2_log <- as.numeric(data$rtv2_log)
```

```{r,echo=FALSE, warning=FALSE, message=FALSE}
data = apply_labels(data,
                    c3_childage2 = "Age",
                    group_dich = "Group",
                    #group_dich = c("ADHD" = 1,
                                   #"Control" = 0),
                    sex = "Sex",
                    #sex = c("Female" = 1,
                            #"Male" = 0),
                    p3medcur = "Medication Status",
                    handed = "Handedness",
                    c1_iq_sts = "FSIQ",
                    IRSADScore = "SES",
                    L_SLF2_tbv = "Left SLF2 Volume",
                    L_SLF2_AFD_m = "Left SLF2 AFD",
                    rt2_log = "N-Back Reaction Time (RT)",
                    rtv2_log = "N-Back RT Variability",
                    c3_nback_b_total_misses_2 = "Misses",
                    c3_nback_b_d_2 = "d-prime (d')",
                    c3_nback_b_c_2 = "c",
                    c3_nback_b_total_fa_2 = "False Alarms",
                    c3_nback_b_bl1_hit_rt_2 = "Reaction Time",
                    c3_nback_b_bl1_hit_rtvar_2 = "Reaction Time Variability")
data$c3_nback_b_total_fa_2
```
#Working Memory Distributions
#Misses
```{r}
vp_tm <- ggplot(data, aes(x=group_dich, y=c3_nback_b_total_misses_2, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Misses") + 
  scale_x_discrete(name = "")
vp_tm <- vp_tm + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Total Misses")

legend_title <- "Group"
vp_tm <- vp_tm + theme(legend.position = "none")
vp_tm
ggsave("vp_tm.png")
```

#d-Prime
```{r}
vp_dp <- ggplot(data, aes(x=group_dich, y=c3_nback_b_d_2, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "d-Prime") + 
  scale_x_discrete(name = "")
vp_dp <- vp_dp + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "d-Prime")
legend_title <- "Group"
vp_dp <- vp_dp + theme(legend.position = "none")
vp_dp
ggsave("vp_dp.png")
```
#c
```{r}
vp_c <- ggplot(data, aes(x=group_dich, y=c3_nback_b_c_2, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "c") + 
  scale_x_discrete(name = "")
vp_c <- vp_c + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "c")
legend_title <- "Group"
vp_c <- vp_c + theme(legend.position = "none")
vp_c
ggsave("vp_c.png")
```
#total fa
```{r}
vp_tfa <- ggplot(data, aes(x=group_dich, y=c3_nback_b_total_fa_2, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Total False Alarms") + 
  scale_x_discrete(name = "")
vp_tfa <- vp_tfa + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Total False Alarms")
legend_title <- "Group"
vp_tfa <- vp_tfa + theme(legend.position = "none")
vp_tfa
ggsave("vp_tfa.png")
```
#Reaction Time
```{r}
vp_rt <- ggplot(data, aes(x=group_dich, y=c3_nback_b_bl1_hit_rt_2, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Reaction Time") + 
  scale_x_discrete(name = "")
vp_rt <- vp_rt + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Reaction Time")
legend_title <- "Group"
vp_rt <- vp_rt + theme(legend.position = "none")
vp_rt
ggsave("vp_rt.png")
```
#Reaction Time
```{r}
vp_rtv <- ggplot(data, aes(x=group_dich, y=c3_nback_b_bl1_hit_rtvar_2, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Reaction Time Variability") + 
  scale_x_discrete(name = "")
vp_rtv <- vp_rtv + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Reaction Time Variability")
legend_title <- "Group"
vp_rtv <- vp_rtv + theme(legend.position = "none")
vp_rtv
ggsave("vp_rtv.png")
```
#SLF Distributions
#L_SLF1_AFD_m
```{r}
vp_lslf1_afd <- ggplot(data, aes(x=group_dich, y=L_SLF1_AFD_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFI AFD") + 
  scale_x_discrete(name = "")
vp_lslf1_afd <- vp_lslf1_afd + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFI AFD")
legend_title <- "Group"
vp_lslf1_afd <- vp_lslf1_afd + theme(legend.position = "none")
vp_lslf1_afd
ggsave("vp_lslf1_afd.png")
```
#L_SLF2_AFD_m
```{r}
vp_lslf2_afd <- ggplot(data, aes(x=group_dich, y=L_SLF2_AFD_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFII AFD") + 
  scale_x_discrete(name = "")
vp_lslf2_afd <- vp_lslf2_afd + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFII AFD")
legend_title <- "Group"
vp_lslf2_afd <- vp_lslf2_afd + theme(legend.position = "none")
vp_lslf2_afd
ggsave("vp_lslf2_afd.png")
```
#L_SLF3_AFD_m
```{r}
vp_lslf3_afd <- ggplot(data, aes(x=group_dich, y=L_SLF3_AFD_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFIII AFD") + 
  scale_x_discrete(name = "")
vp_lslf3_afd <- vp_lslf3_afd + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFIII AFD")
legend_title <- "Group"
vp_lslf3_afd <- vp_lslf3_afd + theme(legend.position = "none")
vp_lslf3_afd
ggsave("vp_lslf3_afd.png")
```
#R_SLF1_AFD_m
```{r}
vp_rslf1_afd <- ggplot(data, aes(x=group_dich, y=R_SLF1_AFD_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFI AFD") + 
  scale_x_discrete(name = "")
vp_rslf1_afd <- vp_rslf1_afd + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFI AFD")
legend_title <- "Group"
vp_rslf1_afd <- vp_rslf1_afd + theme(legend.position = "none")
vp_rslf1_afd
ggsave("vp_rslf1_afd.png")
```

#R_SLF2_AFD_m
```{r}
vp_rslf2_afd <- ggplot(data, aes(x=group_dich, y=R_SLF2_AFD_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFII AFD") + 
  scale_x_discrete(name = "")
vp_rslf2_afd <- vp_rslf2_afd + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFII AFD")
legend_title <- "Group"
vp_rslf2_afd <- vp_rslf2_afd + theme(legend.position = "none")
vp_rslf2_afd
ggsave("vp_rslf2_afd.png")
```

#R_SLF3_AFD_m
```{r}
vp_rslf3_afd <- ggplot(data, aes(x=group_dich, y=R_SLF3_AFD_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFIII AFD") + 
  scale_x_discrete(name = "")
vp_rslf3_afd <- vp_rslf3_afd + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFIII AFD")
legend_title <- "Group"
vp_rslf3_afd <- vp_rslf3_afd + theme(legend.position = "none")
vp_rslf3_afd
ggsave("vp_rslf3_afd.png")
```



#L_SLF1_FA_m
```{r}
vp_lslf1_FA <- ggplot(data, aes(x=group_dich, y=L_SLF1_bin_FA_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFI FA") + 
  scale_x_discrete(name = "")
vp_lslf1_FA <- vp_lslf1_FA + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFI FA")
legend_title <- "Group"
vp_lslf1_FA <- vp_lslf1_FA + theme(legend.position = "none")
vp_lslf1_FA
ggsave("vp_lslf1_FA.png")
```
#L_SLF2_FA_m
```{r}
vp_lslf2_FA <- ggplot(data, aes(x=group_dich, y=L_SLF2_bin_FA_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFII FA") + 
  scale_x_discrete(name = "")
vp_lslf2_FA <- vp_lslf2_FA + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFII FA")
legend_title <- "Group"
vp_lslf2_FA <- vp_lslf2_FA + theme(legend.position = "none")
vp_lslf2_FA
ggsave("vp_lslf2_FA.png")
```
#L_SLF3_FA_m
```{r}
vp_lslf3_FA <- ggplot(data, aes(x=group_dich, y=L_SLF3_bin_FA_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFIII FA") + 
  scale_x_discrete(name = "")
vp_lslf3_FA <- vp_lslf3_FA + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFIII FA")
legend_title <- "Group"
vp_lslf3_FA <- vp_lslf3_FA + theme(legend.position = "none")
vp_lslf3_FA
ggsave("vp_lslf3_FA.png")
```
#R_SLF1_FA_m
```{r}
vp_rslf1_FA <- ggplot(data, aes(x=group_dich, y=R_SLF1_bin_FA_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFI FA") + 
  scale_x_discrete(name = "")
vp_rslf1_FA <- vp_rslf1_FA + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFI FA")
legend_title <- "Group"
vp_rslf1_FA <- vp_rslf1_FA + theme(legend.position = "none")
vp_rslf1_FA
ggsave("vp_rslf1_FA.png")
```

#R_SLF2_FA_m
```{r}
vp_rslf2_FA <- ggplot(data, aes(x=group_dich, y=R_SLF2_bin_FA_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFII FA") + 
  scale_x_discrete(name = "")
vp_rslf2_FA <- vp_rslf2_FA + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFII FA")
legend_title <- "Group"
vp_rslf2_FA <- vp_rslf2_FA + theme(legend.position = "none")
vp_rslf2_FA
ggsave("vp_rslf2_FA.png")
```

#R_SLF3_FA_m
```{r}
vp_rslf3_FA <- ggplot(data, aes(x=group_dich, y=R_SLF3_bin_FA_m, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFIII FA") + 
  scale_x_discrete(name = "")
vp_rslf3_FA <- vp_rslf3_FA + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFIII FA")
legend_title <- "Group"
vp_rslf3_FA <- vp_rslf3_FA + theme(legend.position = "none")
vp_rslf3_FA
ggsave("vp_rslf3_FA.png")
```

#L_SLF1_bin_vol
```{r}
vp_lslf1_bin_vol <- ggplot(data, aes(x=group_dich, y=L_SLF1_bin_vol, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFI Volume") + 
  scale_x_discrete(name = "")
vp_lslf1_bin_vol <- vp_lslf1_bin_vol + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFI Volume")
legend_title <- "Group"
vp_lslf1_bin_vol <- vp_lslf1_bin_vol + theme(legend.position = "none")
vp_lslf1_bin_vol
ggsave("vp_lslf1_vol.png")
```
#L_SLF2_bin_vol
```{r}
vp_lslf2_bin_vol <- ggplot(data, aes(x=group_dich, y=L_SLF2_bin_vol, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFII Volume") + 
  scale_x_discrete(name = "")
vp_lslf2_bin_vol <- vp_lslf2_bin_vol + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFII Volume")
legend_title <- "Group"
vp_lslf2_bin_vol <- vp_lslf2_bin_vol + theme(legend.position = "none")
vp_lslf2_bin_vol
ggsave("vp_lslf2_vol.png")
```
#L_SLF3_bin_vol
```{r}
vp_lslf3_bin_vol <- ggplot(data, aes(x=group_dich, y=L_SLF3_bin_vol, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Left SLFIII Volume") + 
  scale_x_discrete(name = "")
vp_lslf3_bin_vol <- vp_lslf3_bin_vol + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Left SLFIII Volume")
legend_title <- "Group"
vp_lslf3_bin_vol <- vp_lslf3_bin_vol + theme(legend.position = "none")
vp_lslf3_bin_vol
ggsave("vp_lslf3_vol.png")
```
#R_SLF1_bin_vol
```{r}
vp_rslf1_bin_vol <- ggplot(data, aes(x=group_dich, y=R_SLF1_bin_vol, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFI Volume") + 
  scale_x_discrete(name = "")
vp_rslf1_bin_vol <- vp_rslf1_bin_vol + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFI Volume")
legend_title <- "Group"
vp_rslf1_bin_vol <- vp_rslf1_bin_vol + theme(legend.position = "none")
vp_rslf1_bin_vol
ggsave("vp_rslf1_vol.png")
```

#R_SLF2_bin_vol
```{r}
vp_rslf2_bin_vol <- ggplot(data, aes(x=group_dich, y=R_SLF2_bin_vol, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFII Volume") + 
  scale_x_discrete(name = "")
vp_rslf2_bin_vol <- vp_rslf2_bin_vol + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFII Volume")
legend_title <- "Group"
vp_rslf2_bin_vol <- vp_rslf2_bin_vol + theme(legend.position = "none")
vp_rslf2_bin_vol
ggsave("vp_rslf2_vol.png")
```

#R_SLF3_bin_vol
```{r}
vp_rslf3_bin_vol <- ggplot(data, aes(x=group_dich, y=R_SLF3_bin_vol, colour=group_dich)) + 
  geom_violin(alpha = 0.5) +
  geom_quasirandom() + 
  theme(legend.position = "none") +
  scale_y_continuous(name = "Right SLFIII Volume") + 
  scale_x_discrete(name = "")
vp_rslf3_bin_vol <- vp_rslf3_bin_vol + geom_boxplot(width=0.06) + 
  stat_summary(fun.y=mean, geom="point", shape=2, size=2, colour="blue") +
  stat_summary(fun.y=median, geom="point", size=2, color="purple") + 
  scale_color_brewer(palette="Dark2") +
  labs(title= "Right SLFIII Volume")
legend_title <- "Group"
vp_rslf3_bin_vol <- vp_rslf3_bin_vol + theme(legend.position = "none")
vp_rslf3_bin_vol
ggsave("vp_rslf3_vol.png")
```
#Play plotting
```{r}
#vp_tm + stat_summary(fun.data="mean_sdl", mult=1, 
#                 geom="crossbar", width=0.2 )
 
#vp_tm + stat_summary(fun.data=mean_sdl, mult=1, 
#                 geom="pointrange", color="purple")

#vp_tm + geom_dotplot(binaxis='y', stackdir='center', dotsize=1)
```


```{r}
#plot_tm <- ggplot(data, aes(x = group_dich, y = c3_nback_b_total_misses_2)) +
#  geom_violin(alpha = 0.5) +
# geom_quasirandom() +
#  theme(legend.position = "none") + 
#  scale_y_continuous(name = "Misses") + 
#  scale_x_continuous(name = "ID") +
#  theme_pubr() +
#  theme(legend.position = c(0.9, .9))
```

